Solutions to Integer Programming from Quantum Annealing

### 2020-09-12 paper/main.tex
some acknowledgements and filled out affiliations

\author{Chia~Cheng~Chang (\begin{CJK*}{UTF8}{bsmi}張家丞\end{CJK*})}
\affiliation{RIKEN iTHEMS, Wako, Saitama 351-0198, Japan}
\affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
	\author{Chih-Chieh~Chen }
\affiliation{R\&D Group, Grid Inc., Tokyo 107-0061, Japan}
\author{Christopher K\"orber}
\affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
\author{Travis~Humble}
\affiliation{Quantum Computing Institute, Oak Ridge National Laboratory, Oak Ridge, Tennessee 37831, USA}
\author{Jim~Ostrowski}
\affiliation{University of Tennessee}

@@

We thank Long Gang Pang for inspiring discussions.

>>>>

\author{Chia~Cheng~Chang}
\affiliation{RIKEN iTHEMS, Wako, Saitama 351-0198, Japan}
\affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
	\author{Chih-Chieh~Chen }
\affiliation{R\&D Group, Grid Inc., Tokyo 107-0061, Japan}
\affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
\author{Christopher K\"orber}
\affiliation{Institut f\"ur Theoretische Physik II, Ruhr-Universit\"at Bochum, D-44780 Bochum, Germany}
\affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
\author{Travis~Humble}
\affiliation{Quantum Computing Institute, Oak Ridge National Laboratory, Oak Ridge, Tennessee 37831, USA}
\affiliation{Computational Sciences and Engineering, Oak Ridge National Laboratory, Oak Ridge, Tennessee, 37831, USA}
\author{Jim~Ostrowski}
\affiliation{Industrial and Systems Engineering, University of Tennessee, Knoxville, Tennessee 37996, USA}

@@

We thank Long Gang Pang for inspiring discussions.
We thank David Johnson, Vlad Papish and the rest of D-Wave Support for answering detailed questions about the D-Wave annealer.
